### 2014-04-23 paper/introduction.tex
fix orphans, add text about automatic plane cut

\section{Introduction}
Makers, researchers, and professional designers (jointly ``makers" for the remainder of this paper) increasingly leverage 3D printers as tools for design work.  A wide array of objects, ranging from toy figurines to video game controllers and jet engine blades, are now prototyped, and sometimes even manufactured, using these machines.  Most models fabricated on 3D printers today are passive: they express the form, but not the interactivity, of an object.

@@

Figure \ref{fig:teaser} shows a collection of interactive objects fabricated with the help of internal pipes. These objects can sense touch, detect object presence, generate haptic feedback, or show internal illumination. They could also contain other active and passive electronic components. However, manually modeling appropriate pipes for such functionality is not trivial.  For one, many 3D modelling tools do not provide extensive tools for modelling the  {\em interior} of 3D models. Furthermore, careful consideration needs to go into the design and routing of pipes when they are used to add interactivity. Pipes need maximum possible bend radius to ease the insertion of media post-print.  Independent pipes cannot intersect, as this could lead to electrical shorting or other problems.  Pipes should not pass too close to the surface: consumer-grade 3D printers do not guarantee air- or water-tightness of prints, so more than one printed layer may be required to prevent leakage.  Pipes for applications like illuminated EL wire signs must allow a single pipe to follow a specific path layout (e.g., for spelling out text).

We contribute PipeDream, an interactive design tool for interior pipes. Our system addresses the various challenges that makers are likely to encounter, such as avoiding intersections and ensuring maximum bend angles. PipeDream offers 3D point-to-point routing of internal pipes based on physical simulation of flexible rods, and a graph algorithm-based path tracing technique to create shape-constrained internal paths. We present a set of example objects, designed with the help of our modeling tool, that demonstrate different interaction modalities. We conclude by discussing limitations and outlining areas for future exploration.

>>>>

\section{Introduction}
Makers, researchers, and professional designers (jointly ``makers" in this paper) increasingly leverage 3D printers as tools for design work.  A wide array of objects, from toy figurines to video game controllers and jet engine blades, are now prototyped or even manufactured using these machines.  Most models fabricated on 3D printers today are passive: they express the form, but not the interactivity, of an object.

@@

Figure \ref{fig:teaser} shows a collection of interactive objects fabricated with the help of internal pipes. These objects can sense touch, detect object presence, generate haptic feedback, or show internal illumination. They could also contain other active and passive electronic components. However, manually modeling appropriate pipes for such functionality is not trivial.  For one, many 3D modelling tools do not provide extensive tools for modelling the  {\em interior} of 3D models. Furthermore, careful consideration needs to go into the design and routing of pipes when they are used to add interactivity. Pipes need maximum possible bend radius to ease the insertion of media post-print.  Independent pipes cannot intersect, as this could lead to electrical shorting or other problems.  Pipes should not pass too close to the surface: consumer-grade 3D printers do not guarantee air- or water-tightness of prints, so more than one printed layer may be required to prevent leakage.  Pipes for applications like illuminated EL wire signs must allow a single pipe to follow a specific path (e.g., for writing text).

We contribute PipeDream, an interactive design tool for interior pipes. Our system addresses various challenges makers are likely to encounter, such as avoiding intersections and ensuring maximum bend angles. PipeDream offers 3D point-to-point routing of internal pipes based on physical simulation of flexible rods, and a graph algorithm-based path tracing technique for path-constrained pipes. We present a set of example objects, designed with the help of our tool, that demonstrate different interaction modalities. We conclude by discussing limitations and outlining areas for future exploration.

### 2014-04-23 paper/tubes.tex
resize figure abcs, change caption of radius figure
fix orphans, add text about automatic plane cut

\begin{figure}
\centering
    \includegraphics[width=3.4in]{figures/radius.png}
\caption{A user whose pipe has too small a radius (a) can adjust it with a slider (b) to be larger (c).  PipeDream's live preview shows the real size and location of the cut before it is committed to the mesh.}
\label{fig:radius}
\end{figure}

@@

{\bf Eulerization:} In order to make our graph Eulerian, we consider all odd degree vertices in the connected graph and make a clique of potential edges based on distance.  We greedily add edges between the odd nodes until no odd nodes remain.  Finally, we remove our temporary edge, changing the graph from Eulerian to semi-Eulerian.  This is a connected, semi-Eulerian graph which contains all edges in the input.
A lower total weight matching may be possible by connecting components and ensuring node evenness together in a global process, as well as by using minimum-weight matching rather than greedy selection, however this optimization is not crucial for our purposes.

@@

@@

\section{Fabrication Techniques}
Several pragmatic concerns arise when fabricating models with hollow pipes and cavities on additive manufactuing machines. Pipes frequently lead to overhangs (where an underlying supporting layer has a smaller footprint than the subsequent layer).
%Beyond design, the tubes must actually be printable to be useful.  
%When geometries contain overhangs, as there may be in designed pipes and cavities, 
To allow overhangs, 3D printers may lay down support material that must be later removed from the model.  The removal process can be time-intensive and challenging.  The physical fabrication process used by different machines gives rise to differing strategies for avoiding support material or easing its removal.  We next discuss techniques for fused deposition modeling (FDM) machines, such as the Makerbot\footnote{\url{http://makerbot.com}} and polyjet machines such as Stratasys Connex\footnote{\url{http://stratasys.com}}, as well as powder-based machines (e.g., ZCorp\footnote{\url{http://3dsystems.com}}) and those that use stereolithography (e.g., Form 1\footnote{\url{http://formlabs.com}}).

@@

\subsection{Model Assembly}
For especially complex geometries, models can be ``cut up'' into multiple pieces that can be assembled to avoid support deposition or at least ease material removal; it can also ease insertion of the desired medium. This is somewhat undesirable as it means more time spent in assembly post-print, and additionally a cut pipe may no longer be fluid-tight.  A tool aiding in or automatically performing this cutting task might be beneficial, however it is outside the scope of this work.

>>>>

\begin{figure}
\centering
    \includegraphics[width=3.4in]{figures/radius.png}
\caption{Users can interactively change the radius of their pipes using a slider (b).  PipeDream's live preview shows the real size and location of the cut before it is committed to the mesh.}
\label{fig:radius}
\end{figure}

@@

{\bf Eulerization:} In order to make our graph Eulerian, we consider all odd-degree vertices in the connected graph and make a clique of potential edges based on distance.  We greedily add edges between odd nodes until no odd nodes remain.  Finally, we remove our temporary edge, changing the graph from Eulerian to semi-Eulerian.  This is a connected, semi-Eulerian graph that contains all edges in the input.
A lower total weight matching is possible by connecting components and ensuring node evenness together in a global process, as well as by using minimum-weight matching rather than greedy selection, however this optimization is not crucial for our purposes.

@@

\subsubsection{Separating at the Pipe Plane}
We allow users the choice to separate their meshes at the pipe plane, which may be necessary for support material removal (discussed later) or insertion of media: e.g., EL wire can be bent much more sharply by hand in the plane than it can by pushing from one end into a pipe.  To do this, we simply perform a plane cut after the mesh modification operation described below.

@@

\section{Fabrication Techniques}
Several pragmatic concerns arise when fabricating models with hollow pipes and cavities on additive manufactuing machines. Pipes frequently lead to overhangs (where an underlying supporting layer has a smaller footprint than the subsequent layer).
To allow overhangs, 3D printers may lay down support material that must be later removed from the model.  The removal process can be time-intensive and challenging.  The physical fabrication process used by different machines gives rise to differing strategies for avoiding support material or easing its removal.  We next discuss techniques for fused deposition modeling (FDM) machines, such as the Makerbot\footnote{\url{http://makerbot.com}} and polyjet machines such as Stratasys Connex\footnote{\url{http://stratasys.com}}, as well as powder-based machines (e.g., ZCorp\footnote{\url{http://3dsystems.com}}) and those that use stereolithography (e.g., Form 1\footnote{\url{http://formlabs.com}}).

@@

\subsection{Model Assembly}
For especially complex geometries, models can be ``cut up'' into multiple pieces that can be assembled to avoid support deposition or at least ease material removal; it can also ease insertion of the desired medium. This is somewhat undesirable as it means more time spent in assembly post-print, and additionally a cut pipe may no longer be fluid-tight.  Our plane cut option goes towards this, however a more advanced tool for this purpose is outside the scope of this work.
